A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2020-12-09 kobakian-cook.Rmd

>>>>

<!-- When the algorithm is applied to the complete set of all Australian Statistical Areas at Level 2 it results in the hexagon tile map display shown in Figure \ref{fig:hexmap}. This display highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Hobart. This display also highlights the disparity in the burden of thyroid cancer for females in the communities of these cities. There are several collections of red hexagons in Sydney that represent the communities with much higher rates of diagnosis than the Australian average. Brisbane also experiences higher than average rates of diagnosis, but has more orange than red. The females in the cities of Adelaide and Perth  show much lower rates of diagnosis. -->

<!-- Compared to the choropleth map display, the low rates in the rural Australian communities are no longer dominating the display. While the representative hexagons are still visible against the black background, the much lower than average rates in the Northern Territory are less noticeable. -->
